---
title: "Study 2"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: default
---

## (1) Description of Data

The posted data for this study consists of 1 compiled, deidentified data file. The lexical decision task data was cleaned and scored in Excel according to procedures from Lisjak et al., 2012, Study 2:

* Total trials before cleaning: 7040
* Total error trials removed: 341 (`r round((341/7040)*100, digits=2)`%)
* Total extreme responses (>3500ms) removed: 4 (`r round((4/7040)*100, digits=2)`%)
* Total outliers removed (after removing errors and extreme responses): 126 (`r round((126/7040)*100, digits=2)`%)\
\

```{r include=FALSE}
options(width=100)

library(RCurl)
library(plyr)
library(ggplot2)
library(pequod)
library(psych)
library(data.table)
library(rtf)
library(pwr)

## DATA PREPARATION ##
csv <- getURL("https://raw.githubusercontent.com/abrowman/ism-jpsp2017/master/Study%202/ISM_Study2.csv")
mydata <- read.csv(textConnection(csv))

mydata$cond_c <- scale(ifelse(mydata$cond=="student", 1, ifelse(mydata$cond=="friend", 2, NA)), scale=F, center=T)
options(contrasts=c("contr.sum","contr.poly"))
attach(mydata)

# score measures
rfs.pro <- (RFSpro2+RFSpro3+RFSpro4+RFSpro5)/4
rfs.pre <- (RFSpre1+RFSpre2+RFSpre3+RFSpre5)/4
rfs <- rfs.pro-rfs.pre
rfs_c <- scale(rfs,scale=F,center=T)

rfb.pro <- (RFBpro2+RFBpro3+RFBpro4+RFBpro5)/4
rfb.pre <- (RFBpre1+RFBpre2+RFBpre3+RFBpre5)/4
rfb <- rfb.pro-rfb.pre
rfb_c <- scale(rfb,scale=F,center=T)

rfq.pro <- ((6-RFQpro1r)+RFQpro2+RFQpro3+(6-RFQpro4r)+RFQpro5+(6-RFQpro6r))/6
rfq.pre <- ((6-RFQpre1r)+(6-RFQpre2r)+RFQpre3+(6-RFQpre4r)+(6-RFQpre5r))/5
rfq <- rfq.pro-rfq.pre
rfq_c <- scale(rfq,scale=F,center=T)

rfprimed <- ifelse(cond=="student", rfs, ifelse(cond=="friend", rfb, NA))
rfnonprimed <- ifelse(cond=="student", rfb, ifelse(cond=="friend", rfs, NA))

promolog_c <- scale(promolog,scale=F,center=T)
prevlog_c <- scale(prevlog,scale=F,center=T)
promo_c <- scale(promo,scale=F,center=T)
prev_c <- scale(prev,scale=F,center=T)
rfprimed_c <- scale(rfprimed,scale=F,center=T)
rfnonprimed_c <- scale(rfnonprimed,scale=F,center=T)
```


## (2) Descriptive Statistics

**Total *N*:** `r nrow(mydata)`

**Sensitivity analysis:** This sample provided a statistical power of .80 to detect effects of *f*^2^ >= `r round(pwr.f2.test(u = 1, v = nrow(mydata)-2, sig.level = .05, power = .80)$f2, digits = 3)`.

**Percentage by gender:**
```{r echo=FALSE}
gender <- factor(ifelse(Gender==1, "male", ifelse(Gender==2, "female", NA)))
table(gender, useNA="always")
```

***N* in each condition:**
```{r echo=FALSE}
table(cond, useNA="always")
```

***M*s and *SD*s:**
```{r echo=FALSE}
describe(data.frame(Age,rfs,rfs.pro,rfs.pre,rfb,rfb.pro,rfb.pre,rfq,rfq.pro,rfq.pre))[c(2,3,4)]
```

**Alphas:**  

* **Identity-specific motivation-academics promotion:** `r round(alpha(data.frame(RFSpro2,RFSpro3,RFSpro4,RFSpro5))$total$raw_alpha, digits=2)`
* **Identity-specific motivation-academics prevention:** `r round(alpha(data.frame(RFSpre1,RFSpre2,RFSpre3,RFSpre5))$total$raw_alpha, digits=2)`
* **Identity-specific motivation-friend promotion:** `r round(alpha(data.frame(RFBpro2,RFBpro3,RFBpro4,RFBpro5))$total$raw_alpha, digits=2)`
* **Identity-specific motivation-friend prevention:** `r round(alpha(data.frame(RFBpre1,RFBpre2,RFBpre3,RFBpre5))$total$raw_alpha, digits=2)`
* **RFQ promotion:** `r round(alpha(data.frame((6-RFQpro1r),RFQpro2,RFQpro3,(6-RFQpro4r),RFQpro5,(6-RFQpro6r)))$total$raw_alpha, digits=2)`
* **RFQ prevention:** `r round(alpha(data.frame((6-RFQpre1r),(6-RFQpre2r),RFQpre3,(6-RFQpre4r),(6-RFQpre5r)))$total$raw_alpha, digits=2)`


## (3) Correlations

**Correlations:**
```{r echo=FALSE}
corlist <- data.frame(rfs,rfb,rfq)
cortable <- data.frame(round(corr.test(as.matrix(corlist))$ci[,1:3], digits=2), round(corr.test(as.matrix(corlist))$ci[,4], digits=4), corr.test(as.matrix(corlist))$n[c(2,3,6)]-2)
colnames(cortable) <- c("lower","r","upper","p","df")
cortable
```


## (4) Random assignment checks

**(a) Unequal variance test, *t*-test, and *M*s and *SD*s for: identity-specific motivation-student**
```{r echo=FALSE}
var.test(rfs~cond)
t.test(rfs~cond, var.equal=FALSE)
describeBy(rfs, mydata$cond)
```

**(b) Unequal variance test, *t*-test, and *M*s and *SD*s for: identity-specific motivation-friend**
```{r echo=FALSE}
var.test(rfb~cond)
t.test(rfb~cond, var.equal=TRUE)
describeBy(rfb, mydata$cond)
```

**(c) Unequal variance test, *t*-test, and *M*s and *SD*s for: RFQ**
```{r echo=FALSE}
var.test(rfq~cond)
t.test(rfq~cond, var.equal=TRUE)
describeBy(rfq, mydata$cond)
```


## (5) Main Analyses

#### Promotion analyses

**Estimates and CIs:**
```{r echo=FALSE}
summary(promo.active.regress <- lm(promolog ~ rfprimed_c + rfnonprimed_c + rfq_c + prevlog_c))
round(confint(promo.active.regress, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for identity-specific motivation-primed:** `r round((summary(promo.active.regress)$r.squared-summary(lm(promolog ~ rfnonprimed_c + rfq_c + prevlog_c))$r.squared)/(1-summary(promo.active.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for identity-specific motivation-nonprimed:** `r round((summary(promo.active.regress)$r.squared-summary(lm(promolog ~ rfprimed_c + rfq_c + prevlog_c))$r.squared)/(1-summary(promo.active.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for RFQ:** `r round((summary(promo.active.regress)$r.squared-summary(lm(promolog ~ rfprimed_c + rfnonprimed_c + prevlog_c))$r.squared)/(1-summary(promo.active.regress)$r.squared), digits=3)`  
\  

#### Prevention analyses

**Estimates and CIs:**
```{r echo=FALSE}
summary(prev.active.regress <- lm(prevlog ~ rfprimed_c + rfnonprimed_c + rfq_c + promolog_c))
round(confint(prev.active.regress, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for identity-specific motivation-primed:** `r round((summary(prev.active.regress)$r.squared-summary(lm(prevlog ~ rfnonprimed_c + rfq_c + promolog_c))$r.squared)/(1-summary(prev.active.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for identity-specific motivation-nonprimed:** `r round((summary(prev.active.regress)$r.squared-summary(lm(prevlog ~ rfprimed_c + rfq_c + promolog_c))$r.squared)/(1-summary(prev.active.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for RFQ:** `r round((summary(prev.active.regress)$r.squared-summary(lm(prevlog ~ rfprimed_c + rfnonprimed_c + promolog_c))$r.squared)/(1-summary(prev.active.regress)$r.squared), digits=3)`


## (6) Plots

These plots use non-logged RTs and non-centered values for visualization purposes.

### Promotion plot

```{r echo=FALSE, warning=FALSE}
promo.plot.regress <- lm(promo ~ rfprimed + rfnonprimed + rfq + prev)
promo.plot.coefs <- coefficients(promo.plot.regress)

promo.rfprimed.minus1 <- promo.plot.coefs[1] + (promo.plot.coefs[2]*(mean(rfprimed, na.rm=T)-sd(rfprimed, na.rm=T))) + (promo.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (promo.plot.coefs[4]*(mean(rfq, na.rm=T))) + (promo.plot.coefs[5]*(mean(prev, na.rm=T)))
promo.rfprimed.plus1 <- promo.plot.coefs[1] + (promo.plot.coefs[2]*(mean(rfprimed, na.rm=T)+sd(rfprimed, na.rm=T))) + (promo.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (promo.plot.coefs[4]*(mean(rfq, na.rm=T))) + (promo.plot.coefs[5]*(mean(prev, na.rm=T)))

promo.rfnonprimed.minus1 <- promo.plot.coefs[1] + (promo.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (promo.plot.coefs[3]*(mean(rfnonprimed, na.rm=T)-sd(rfnonprimed, na.rm=T))) + (promo.plot.coefs[4]*(mean(rfq, na.rm=T))) + (promo.plot.coefs[5]*(mean(prev, na.rm=T)))
promo.rfnonprimed.plus1 <- promo.plot.coefs[1] + (promo.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (promo.plot.coefs[3]*(mean(rfnonprimed, na.rm=T)+sd(rfnonprimed, na.rm=T))) + (promo.plot.coefs[4]*(mean(rfq, na.rm=T))) + (promo.plot.coefs[5]*(mean(prev, na.rm=T)))

promo.rfq.minus1 <- promo.plot.coefs[1] + (promo.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (promo.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (promo.plot.coefs[4]*(mean(rfq, na.rm=T)-sd(rfq, na.rm=T))) + (promo.plot.coefs[5]*(mean(prev, na.rm=T)))
promo.rfq.plus1 <- promo.plot.coefs[1] + (promo.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (promo.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (promo.plot.coefs[4]*(mean(rfq, na.rm=T)+sd(rfq, na.rm=T))) + (promo.plot.coefs[5]*(mean(prev, na.rm=T)))

promo.plot.data <- data.frame(c("aRFprimed","aRFprimed","bRFnon-primed","bRFnon-primed","cRFQ","cRFQ"), c(promo.rfprimed.minus1, promo.rfprimed.plus1, promo.rfnonprimed.minus1, promo.rfnonprimed.plus1, promo.rfq.minus1, promo.rfq.plus1), c("-1","1","-1","1","-1","1"), c(summary(promo.plot.regress)$coefficients[2,2], summary(promo.plot.regress)$coefficients[2,2], summary(promo.plot.regress)$coefficients[3,2], summary(promo.plot.regress)$coefficients[3,2], summary(promo.plot.regress)$coefficients[4,2], summary(promo.plot.regress)$coefficients[4,2]))
colnames(promo.plot.data) <- c("RF","RT","plusminus","se")
limits <- aes(ymax = RT + se, ymin = RT - se)

promo.plot <- ggplot(data=promo.plot.data, aes(x=plusminus, y=RT, linetype=RF)) + # data to plot
  geom_line(aes(group = RF)) + # add regression line
  geom_errorbar(limits, width=.1) +
  theme_bw(base_family = "Arial", base_size = 16) + # font and font size
  theme(legend.position = c(.15,.92)) + # legend position
  theme(legend.key = element_blank()) + # no border around legend
  theme(legend.title=element_blank()) + # remove legend title
  theme(axis.title.x = element_text(vjust=-0.3)) + # move x-axis label lower
  theme(axis.title.y = element_text(vjust=1.3)) + # move y-axis label left
  theme(panel.grid.minor = element_blank()) + # no grids
  theme(panel.grid.major = element_blank()) + # no borders
  theme(panel.border = element_blank()) + # removes default grey axis lines
  theme(axis.line = element_line(color = 'black')) + # put axis lines back, but in black
  coord_cartesian(ylim=c(600, 700)) + # y-axis range
  scale_linetype_discrete(labels = c("aRFprimed"="RF of focal role", "bRFnon-primed"="RF of non-focal role", "cRFQ"="RFQ"), breaks=c("aRFprimed","bRFnon-primed","cRFQ")) +
  scale_x_discrete("", labels = c("-1"="More prevention-focused\nat pre-testing (-1 SD)", "1"="More promotion-focused\nat pre-testing (+1 SD)")) + # x-axis titles
  scale_y_continuous("Reaction time for promotion words", breaks = seq(600, 700, by = 10)) + # y-axis titles and range
  annotate("text", x=2.5, y=698.5, label="(a)")
promo.plot
ggsave('Figure 1a.png', width=9, height=6, unit='in', dpi=300)
```

### Prevention plot

```{r echo=FALSE, warning=FALSE}
prev.plot.regress <- lm(prev ~ rfprimed + rfnonprimed + rfq + promo)
prev.plot.coefs <- coefficients(prev.plot.regress)

prev.rfprimed.minus1 <- prev.plot.coefs[1] + (prev.plot.coefs[2]*(mean(rfprimed, na.rm=T)-sd(rfprimed, na.rm=T))) + (prev.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (prev.plot.coefs[4]*(mean(rfq, na.rm=T))) + (prev.plot.coefs[5]*(mean(promo, na.rm=T)))
prev.rfprimed.plus1 <- prev.plot.coefs[1] + (prev.plot.coefs[2]*(mean(rfprimed, na.rm=T)+sd(rfprimed, na.rm=T))) + (prev.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (prev.plot.coefs[4]*(mean(rfq, na.rm=T))) + (prev.plot.coefs[5]*(mean(promo, na.rm=T)))

prev.rfnonprimed.minus1 <- prev.plot.coefs[1] + (prev.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (prev.plot.coefs[3]*(mean(rfnonprimed, na.rm=T)-sd(rfnonprimed, na.rm=T))) + (prev.plot.coefs[4]*(mean(rfq, na.rm=T))) + (prev.plot.coefs[5]*(mean(promo, na.rm=T)))
prev.rfnonprimed.plus1 <- prev.plot.coefs[1] + (prev.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (prev.plot.coefs[3]*(mean(rfnonprimed, na.rm=T)+sd(rfnonprimed, na.rm=T))) + (prev.plot.coefs[4]*(mean(rfq, na.rm=T))) + (prev.plot.coefs[5]*(mean(promo, na.rm=T)))

prev.rfq.minus1 <- prev.plot.coefs[1] + (prev.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (prev.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (prev.plot.coefs[4]*(mean(rfq, na.rm=T)-sd(rfq, na.rm=T))) + (prev.plot.coefs[5]*(mean(promo, na.rm=T)))
prev.rfq.plus1 <- prev.plot.coefs[1] + (prev.plot.coefs[2]*(mean(rfprimed, na.rm=T))) + (prev.plot.coefs[3]*(mean(rfnonprimed, na.rm=T))) + (prev.plot.coefs[4]*(mean(rfq, na.rm=T)+sd(rfq, na.rm=T))) + (prev.plot.coefs[5]*(mean(promo, na.rm=T)))

prev.plot.data <- data.frame(c("aRFprimed","aRFprimed","bRFnon-primed","bRFnon-primed","cRFQ","cRFQ"), c(prev.rfprimed.minus1, prev.rfprimed.plus1, prev.rfnonprimed.minus1, prev.rfnonprimed.plus1, prev.rfq.minus1, prev.rfq.plus1), c("-1","1","-1","1","-1","1"), c(summary(prev.plot.regress)$coefficients[2,2], summary(prev.plot.regress)$coefficients[2,2], summary(prev.plot.regress)$coefficients[3,2], summary(prev.plot.regress)$coefficients[3,2], summary(prev.plot.regress)$coefficients[4,2], summary(prev.plot.regress)$coefficients[4,2]))
colnames(prev.plot.data) <- c("RF","RT","plusminus","se")
limits <- aes(ymax = RT + se, ymin = RT - se)

prev.plot <- ggplot(data=prev.plot.data, aes(x=plusminus, y=RT, linetype=RF)) + # data to plot
  geom_line(aes(group = RF)) + # add regression line
  geom_errorbar(limits, width=.1) +
  theme_bw(base_family = "Arial", base_size = 16) + # font and font size
  theme(legend.position = "none") + # legend position
  theme(axis.title.x = element_text(vjust=-0.3)) + # move x-axis label lower
  theme(axis.title.y = element_text(vjust=1.3)) + # move y-axis label left
  theme(panel.grid.minor = element_blank()) + # no grids
  theme(panel.grid.major = element_blank()) + # no borders
  theme(panel.border = element_blank()) + # removes default grey axis lines
  theme(axis.line = element_line(color = 'black')) + # put axis lines back, but in black
  coord_cartesian(ylim=c(600, 700)) + # y-axis range
  scale_linetype_discrete(labels = c("aRFprimed"="RFprimed", "bRFnon-primed"="RFnon-primed", "cRFQ"="RFQ"), breaks=c("aRFprimed","bRFnon-primed","cRFQ")) +
  scale_x_discrete("", labels = c("-1"="More prevention-focused\nat pre-testing (-1 SD)", "1"="More promotion-focused\nat pre-testing (+1 SD)")) + # x-axis titles
  scale_y_continuous("Reaction time for prevention words", breaks = seq(600, 700, by = 10)) + # y-axis titles and range
  annotate("text", x=2.5, y=698.5, label="(b)")
prev.plot
ggsave('Figure 1b.png', width=9, height=6, unit='in', dpi=300)
```


## (7) Supplementary Analyses

### Promotion Analyses

#### Regressing on RT for promotion words on main effects
```{r echo=FALSE}
summary(promo.regress.m1 <- lm(promolog ~ cond_c + rfs_c + rfb_c + rfq_c + prevlog_c))
round(confint(promo.regress.m1, level = 0.95), digits=2)
```

#### Regression with interactions added
```{r echo=FALSE}
summary(promo.regress.m2 <- lm(promolog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfb_c + cond_c:rfq_c + prevlog_c))
round(confint(promo.regress.m2, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for condition x identity-specific motivation-student interaction term:** `r round((summary(promo.regress.m2)$r.squared-summary(lm(promolog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfb_c + cond_c:rfq_c + prevlog_c))$r.squared)/(1-summary(promo.regress.m2)$r.squared), digits=3)`  
***f*<sup>2</sup> value (effect size) for condition x identity-specific motivation-friend interaction term:** `r round((summary(promo.regress.m2)$r.squared-summary(lm(promolog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfq_c + prevlog_c))$r.squared)/(1-summary(promo.regress.m2)$r.squared), digits=3)`

***f*<sup>2</sup> value (effect size) for condition x RFQ interaction term:** `r round((summary(promo.regress.m2)$r.squared-summary(lm(promolog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfb_c + prevlog_c))$r.squared)/(1-summary(promo.regress.m2)$r.squared), digits=3)`


#### Simple effects of identity-specific motivation-student in each condition

**Estimates and CIs:**
```{r echo=FALSE}
contrasts(cond)
promo.lmres <- lmres(promolog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfb_c + cond_c:rfq_c + prevlog_c, mydata)
summary(promo.rfs.ss <- simpleSlope(promo.lmres, pred="rfs_c", mod1="cond_c"))
```

**CIs in the student condition:** `r round(promo.rfs.ss$simple_slope[1,1] + c(-1,1)*promo.rfs.ss$simple_slope[1,2]*qt(0.975, promo.rfs.ss$Df), digits=2)`  

**CIs in the friend condition:** `r round(promo.rfs.ss$simple_slope[2,1] + c(-1,1)*promo.rfs.ss$simple_slope[2,2]*qt(0.975, promo.rfs.ss$Df), digits=2)`


#### Simple effects of identity-specific motivation-friend in each condition

**Estimates and CIs:**
```{r echo=FALSE}
contrasts(cond)
summary(promo.rfb.ss <- simpleSlope(promo.lmres, pred="rfb_c", mod1="cond_c"))
```

**CIs in the student condition:** `r round(promo.rfb.ss$simple_slope[1,1] + c(-1,1)*promo.rfb.ss$simple_slope[1,2]*qt(0.975, promo.rfb.ss$Df), digits=2)`  

**CIs in the friend condition:** `r round(promo.rfb.ss$simple_slope[2,1] + c(-1,1)*promo.rfb.ss$simple_slope[2,2]*qt(0.975, promo.rfb.ss$Df), digits=2)`


#### Simple effects of RFQ in each condition

**Estimates and CIs:**
```{r echo=FALSE}
contrasts(cond)
summary(promo.rfq.ss <- simpleSlope(promo.lmres, pred="rfq_c", mod1="cond_c"))
```

**CIs in the student condition:** `r round(promo.rfq.ss$simple_slope[1,1] + c(-1,1)*promo.rfq.ss$simple_slope[1,2]*qt(0.975, promo.rfq.ss$Df), digits=2)`  

**CIs in the friend condition:** `r round(promo.rfq.ss$simple_slope[2,1] + c(-1,1)*promo.rfq.ss$simple_slope[2,2]*qt(0.975, promo.rfq.ss$Df), digits=2)`


### Prevention Analyses

#### Regressing on RT for prevention words on main effects
```{r echo=FALSE}
summary(prev.regress.m1 <- lm(prevlog ~ cond_c + rfs_c + rfb_c + rfq_c + promolog_c))
round(confint(prev.regress.m1, level = 0.95), digits=2)
```

#### Regression with interactions added
```{r echo=FALSE}
summary(prev.regress.m2 <- lm(prevlog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfb_c + cond_c:rfq_c + promolog_c))
round(confint(prev.regress.m2, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for condition x identity-specific motivation-student interaction term:** `r round((summary(prev.regress.m2)$r.squared-summary(lm(prevlog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfb_c + cond_c:rfq_c + promolog_c))$r.squared)/(1-summary(prev.regress.m2)$r.squared), digits=3)`  
***f*<sup>2</sup> value (effect size) for condition x identity-specific motivation-friend interaction term:** `r round((summary(prev.regress.m2)$r.squared-summary(lm(prevlog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfq_c + promolog_c))$r.squared)/(1-summary(prev.regress.m2)$r.squared), digits=3)`  
***f*<sup>2</sup> value (effect size) for condition x RFQ interaction term:** `r round((summary(prev.regress.m2)$r.squared-summary(lm(prevlog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfb_c + promolog_c))$r.squared)/(1-summary(prev.regress.m2)$r.squared), digits=3)`


#### Simple effects of identity-specific motivation-student in each condition

**Estimates and CIs:**
```{r echo=FALSE}
contrasts(cond)
prev.lmres <- lmres(prevlog ~ cond_c + rfs_c + rfb_c + rfq_c + cond_c:rfs_c + cond_c:rfb_c + cond_c:rfq_c + promolog_c, mydata)
summary(prev.rfs.ss <- simpleSlope(prev.lmres, pred="rfs_c", mod1="cond_c")) # -1 = student; +1 = friend
```

**CIs in the student condition:** `r round(prev.rfs.ss$simple_slope[1,1] + c(-1,1)*prev.rfs.ss$simple_slope[1,2]*qt(0.975, prev.rfs.ss$Df), digits=2)`  

**CIs in the friend condition:** `r round(prev.rfs.ss$simple_slope[2,1] + c(-1,1)*prev.rfs.ss$simple_slope[2,2]*qt(0.975, prev.rfs.ss$Df), digits=2)`


#### Simple effects of identity-specific motivation-friend in each condition

**Estimates and CIs:**
```{r echo=FALSE}
contrasts(cond)
summary(prev.rfb.ss <- simpleSlope(prev.lmres, pred="rfb_c", mod1="cond_c"))
```

**CIs in the student condition:** `r round(prev.rfb.ss$simple_slope[1,1] + c(-1,1)*prev.rfb.ss$simple_slope[1,2]*qt(0.975, prev.rfb.ss$Df), digits=2)`  

**CIs in the friend condition:** `r round(prev.rfb.ss$simple_slope[2,1] + c(-1,1)*prev.rfb.ss$simple_slope[2,2]*qt(0.975, prev.rfb.ss$Df), digits=2)`


#### Simple effects of RFQ in each condition

**Estimates and CIs:**
```{r echo=FALSE, warning=FALSE}
contrasts(cond)
summary(prev.rfq.ss <- simpleSlope(prev.lmres, pred="rfq_c", mod1="cond_c"))
```

**CIs in the student condition:** `r round(prev.rfq.ss$simple_slope[1,1] + c(-1,1)*prev.rfq.ss$simple_slope[1,2]*qt(0.975, prev.rfq.ss$Df), digits=2)`  

**CIs in the friend condition:** `r round(prev.rfq.ss$simple_slope[2,1] + c(-1,1)*prev.rfq.ss$simple_slope[2,2]*qt(0.975, prev.rfq.ss$Df), digits=2)`


```{r echo=FALSE}
# scripts for producing tables

# full models
regtable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), round(coef(summary(modellist[[i]])), digits=3))
    assign(paste("ci", i, sep = ""), paste(round(get(paste("b", i, sep=""))[, 1], digits=2), " [", round(confint(modellist[[i]], level = 0.95)[,1], digits=2), ", ", round(confint(modellist[[i]], level = 0.95)[,2], digits=2), "]", sep = ""))
    assign(paste("t", i, sep = ""), round(summary(modellist[[i]])$coefficients[,3], digits=2))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$df[2],each=1+length(labels(modellist[[1]]))))
    assign(paste("p", i, sep = ""), round(summary(modellist[[i]])$coefficients[,4], digits=3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(all.vars(summary(modellist[[i]])$call)[1], ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rnames <- c("Intercept")
  for (j in 1:length(labels(modellist[[1]]))) {
    rnames <- append(rnames, labels(modellist[[1]])[j])
  }
  rownames(complete) <- rnames
  complete <- complete[-1,]
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)  # this can be an .rtf or a .doc
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models1 <- list(promo.active.regress, prev.active.regress)
regtable(models1, "Table 3")
models2 <- list(promo.regress.m1, prev.regress.m1)
regtable(models2, "Table S4 Step 1")
models3 <- list(promo.regress.m2, prev.regress.m2)
regtable(models3, "Table S4 Step 2")

# simple slopes section
sstable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), signif(summary(modellist[[i]])$simple_slope))
    assign(paste("ci", i, sep = ""), paste(get(paste("b", i, sep=""))[, 1], " [", c(signif(get(paste("b", i, sep=""))[1,1] + c(-1,1)*get(paste("b", i, sep=""))[1,2]*qt(0.975, modellist[[i]]$Df), 3)[1], signif(get(paste("b", i, sep=""))[2,1] + c(-1,1)*get(paste("b", i, sep=""))[2,2]*qt(0.975, modellist[[i]]$Df), 3)[1]), ", ", c(signif(get(paste("b", i, sep=""))[1,1] + c(-1,1)*get(paste("b", i, sep=""))[1,2]*qt(0.975, modellist[[i]]$Df), 3)[2], signif(get(paste("b", i, sep=""))[2,1] + c(-1,1)*get(paste("b", i, sep=""))[2,2]*qt(0.975, modellist[[1]]$Df), 3)[2]), "]", sep = ""))
    assign(paste("t", i, sep = ""), signif(get(paste("b", i, sep=""))[,3], 3))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$Df,each=2))
    assign(paste("p", i, sep = ""), signif(get(paste("b", i, sep=""))[,4], 3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(modellist[[i]]$nomY, ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rownames(complete) <- c(row.names(summary(modellist[[i]])$Points)[1], row.names(summary(modellist[[i]])$Points)[2])
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models.ss1 <- list(promo.rfs.ss, prev.rfs.ss)
sstable(models.ss1, "Table S5 Student RF")
models.ss2 <- list(promo.rfb.ss, prev.rfb.ss)
sstable(models.ss2, "Table S5 Best friend RF")
models.ss3 <- list(promo.rfq.ss, prev.rfq.ss)
sstable(models.ss3, "Table S5 RFQ")
```
