---
title: "Study 3b"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: default
---

## (1) Description of Data

The posted data for this study consists of 1 compiled, deidentified data file. This data file does not include data from an additional 79 respondents either because they did not complete the study, they completed the study more than once, or they nominated inappropriate or nongoal-relevant identities (e.g., “evil,” “sentient bag of meat”) or two identities that were very similar to each other (e.g., “Caucasian American” and “White American”).

```{r include=FALSE}
options(width=100)

library(RCurl)
library(plyr)
library(ggplot2)
library(pequod)
library(psych)
library(data.table)
library(rtf)
library(pwr)

## DATA PREPARATION ##
csv <- getURL("https://raw.githubusercontent.com/abrowman/ism-jpsp2017/master/Study%203b/ISM_Study3b.csv")
mydata <- read.csv(textConnection(csv))
attach(mydata)

# score measures
rfqpro <- ((6-Promote1r)+Promote2+Promote3+(6-Promote4r)+Promote5+(6-Promote6r))/6
rfqpre <- ((6-Prevent1r)+(6-Prevent2r)+Prevent3+(6-Prevent4r)+(6-Prevent5r))/5
rfq <- rfqpro-rfqpre
rfq_c <- scale(rfq,scale=F,center=T)

rfapro <- (RFApro2+RFApro3+RFApro4+RFApro5)/4
rfapre <- (RFApre1+RFApre2+RFApre3+RFApre5)/4
rfa <- rfapro-rfapre
rfa_c <- scale(rfa,scale=F,center=T)

rfbpro <- (RFBpro2+RFBpro3+RFBpro4+RFBpro5)/4
rfbpre <- (RFBpre1+RFBpre2+RFBpre3+RFBpre5)/4
rfb <- rfbpro-rfbpre
rfb_c <- scale(rfb,scale=F,center=T)

rfdif <- abs(rfa-rfb)
integration_c <- scale(Integrate,scale=F,center=T)
```


## (2) Descriptive Statistics

**Total *N*:** `r nrow(mydata)`

**Sensitivity analysis:** This sample provided a statistical power of .80 to detect effects of *f*^2^ >= `r round(pwr.f2.test(u = 1, v = nrow(mydata)-2, sig.level = .05, power = .80)$f2, digits = 3)`.

**Percentage by gender:**
```{r echo=FALSE}
gender <- factor(ifelse(Gender==1, "male", ifelse(Gender==2, "female", NA)))
table(gender, useNA="always")
```

***M*s and *SD*s:**
```{r echo=FALSE}
describe(data.frame(Age,Integrate,rfa,rfapro,rfapre,rfb,rfbpro,rfbpre,rfq,rfqpro,rfqpre))[c(2,3,4)]
```

**Alphas:**  

* **Identity-specific motivation-A promotion:** `r round(alpha(data.frame(RFApro2,RFApro3,RFApro4,RFApro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-A prevention:** `r round(alpha(data.frame(RFApre1,RFApre2,RFApre3,RFApre5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-B promotion:** `r round(alpha(data.frame(RFBpro2,RFBpro3,RFBpro4,RFBpro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-B prevention:** `r round(alpha(data.frame(RFBpre1,RFBpre2,RFBpre3,RFBpre5))$total$raw_alpha, digits=2)`  
* **RFQ promotion:** `r round(alpha(data.frame((6-Promote1r),Promote2,Promote3,(6-Promote4r),Promote5,(6-Promote6r)))$total$raw_alpha, digits=2)`  
* **RFQ prevention:** `r round(alpha(data.frame((6-Prevent1r),(6-Prevent2r),Prevent3,(6-Prevent4r),(6-Prevent5r)))$total$raw_alpha, digits=2)`  


## (3) Correlations

**Correlations:**
```{r echo=FALSE}
corlist <- data.frame(rfa,rfb,rfq,rfdif,Integrate)
cortable <- data.frame(round(corr.test(as.matrix(corlist))$ci[c(1,2,5,10),1:3], digits=2), round(corr.test(as.matrix(corlist))$ci[c(1,2,5,10),4], digits=4), corr.test(as.matrix(corlist))$n[c(2,3,8,20)]-2)
colnames(cortable) <- c("lower","r","upper","p","df")
cortable
```


## (4) Main Analyses

### Regressing on identity-specific motivation-A on Identity-specific motivation-B, integration, and their interaction

**Main effects:**
```{r echo=FALSE}
summary(main1 <- lm(rfa ~ rfb_c + integration_c))
```

**Main effects *CI*s:**
```{r echo=FALSE}
round(confint(main1, level = 0.95), digits = 2)
```

**Omnibus test estimates:**
```{r echo=FALSE}
summary(integrate1 <- lm(rfa ~ rfb_c * integration_c))
```

**Omnibus test *CI*s:**
```{r echo=FALSE}
round(confint(integrate1, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for interaction term:** `r round((summary(integrate1)$r.squared-summary(lm(rfa ~ rfb_c + integration_c))$r.squared)/(1-summary(integrate1)$r.squared), digits = 3)`

**Simple slopes:**
```{r echo=FALSE}
integrate1.lmres <- lmres(rfa ~ rfb_c * integration_c, mydata)
summary(integrate1.ss <- simpleSlope(integrate1.lmres, pred="rfb_c", mod1="integration_c"))
```

**CIs among those with low identity integration:** `r round(integrate1.ss$simple_slope[1,1] + c(-1,1)*integrate1.ss$simple_slope[1,2]*qt(0.975, integrate1.ss$Df), digits=2)`  

**CIs among those with high identity integration:** `r round(integrate1.ss$simple_slope[2,1] + c(-1,1)*integrate1.ss$simple_slope[2,2]*qt(0.975, integrate1.ss$Df), digits=2)`


### Regressing on identity-specific motivation-B on Identity-specific motivation-A, integration, and their interaction

**Main effects:**
```{r echo=FALSE}
summary(main2 <- lm(rfb ~ rfa_c + integration_c))
```

**Main effects *CI*s:**
```{r echo=FALSE}
round(confint(main2, level = 0.95), digits = 2)
```

**Omnibus test estimates:**
```{r echo=FALSE}
summary(integrate2 <- lm(rfb ~ rfa_c * integration_c))
```

**Omnibus test *CI*s:**
```{r echo=FALSE}
round(confint(integrate2, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for interaction term:** `r round((summary(integrate2)$r.squared-summary(lm(rfb ~ rfa_c + integration_c))$r.squared)/(1-summary(integrate2)$r.squared), digits = 3)`

**Simple slopes:**
```{r echo=FALSE}
integrate2.lmres <- lmres(rfb ~ rfa_c * integration_c, mydata)
summary(integrate2.ss <- simpleSlope(integrate2.lmres, pred="rfa_c", mod1="integration_c"))
```

**CIs among those with low identity integration:** `r round(integrate2.ss$simple_slope[1,1] + c(-1,1)*integrate2.ss$simple_slope[1,2]*qt(0.975, integrate2.ss$Df), digits=2)`  

**CIs among those with high identity integration:** `r round(integrate2.ss$simple_slope[2,1] + c(-1,1)*integrate2.ss$simple_slope[2,2]*qt(0.975, integrate2.ss$Df), digits=2)`


## (5) Figures
```{r echo=FALSE}
plot.points1 <- data.frame(c("aLo int","aLo int","bHi int","bHi int"), c("aLo rfb","bHi rfb","aLo rfb","bHi rfb"), c(integrate1.ss$Points[1,1], integrate1.ss$Points[1,2], integrate1.ss$Points[2,1], integrate1.ss$Points[2,2]), c(integrate1.ss$simple_slope[1,2], integrate1.ss$simple_slope[1,2], integrate1.ss$simple_slope[2,2], integrate1.ss$simple_slope[2,2]))
colnames(plot.points1) <- c("int","rfb","rfa","se")
limits <- aes(ymax = rfa + se, ymin = rfa - se)

plot1 <- ggplot(data=plot.points1, aes(x=rfb, y=rfa, linetype=int)) + # data to plot
  geom_line(aes(group = int)) + # add regression line
  geom_errorbar(limits, width=.1) +
  theme_bw(base_family = "Arial", base_size = 14) + # font and font size
  theme(legend.position = c(.19,.95)) + # legend position
  theme(legend.key = element_blank()) + # no border around legend
  theme(legend.title = element_blank()) + # remove legend title
  scale_linetype_discrete(breaks=c("bHi int", "aLo int"), labels=c("Higher identity integration (+1 SD)", "Lower identity integration (-1 SD)")) +
  theme(axis.title.x = element_blank()) + # move x-axis label lower
  theme(axis.title.y = element_text(vjust=1.3)) + # move y-axis label left
  theme(panel.grid.minor = element_blank()) + # no grids
  theme(panel.grid.major = element_blank()) + # no borders
  theme(panel.border = element_blank()) + # removes default grey axis lines
  theme(axis.line = element_line(color = 'black')) + # put axis lines back, but in black
  coord_cartesian(ylim=c(-.6, .9)) + # y-axis range
  scale_x_discrete("", labels = c("aLo rfb"="Prevention-focused\n identity #2 (-1 SD)", "bHi rfb"="Promotion-focused\n identity #2 (+1 SD)")) + # x-axis titles
  scale_y_continuous("Promotion focus of identity #1", breaks = seq(-.6, .9, by=.3)) + # y-axis titles and range
  annotate("text", x=2.5, y=.88, label="(b)")
plot1
ggsave('Figure 3b.png', width=9, height=6, unit='in', dpi=300)
```

```{r include=FALSE}
## Scripts for producing tables

# Tables of full models
regtable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), round(coef(summary(modellist[[i]])), digits=3))
    assign(paste("ci", i, sep = ""), paste(round(get(paste("b", i, sep=""))[, 1], digits=2), " [", round(confint(modellist[[i]], level = 0.95)[,1], digits=2), ", ", round(confint(modellist[[i]], level = 0.95)[,2], digits=2), "]", sep = ""))
    assign(paste("t", i, sep = ""), round(summary(modellist[[i]])$coefficients[,3], digits=2))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$df[2],each=1+length(labels(modellist[[1]]))))
    assign(paste("p", i, sep = ""), round(summary(modellist[[i]])$coefficients[,4], digits=3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(all.vars(summary(modellist[[i]])$call)[1], ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rnames <- c("Intercept")
  for (j in 1:length(labels(modellist[[1]]))) {
    rnames <- append(rnames, labels(modellist[[1]])[j])
  }
  rownames(complete) <- rnames
  complete <- complete[-1,]
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)  # this can be an .rtf or a .doc
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models <- list(main1, main2)
regtable(models, "Table 4b Step 1")
models <- list(integrate1, integrate2)
regtable(models, "Table 4b Step 2")

# Tables for simple slopes
sstable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), signif(summary(modellist[[i]])$simple_slope))
    assign(paste("ci", i, sep = ""), paste(get(paste("b", i, sep=""))[, 1], " [", c(signif(get(paste("b", i, sep=""))[1,1] + c(-1,1)*get(paste("b", i, sep=""))[1,2]*qt(0.975, modellist[[i]]$Df), 3)[1], signif(get(paste("b", i, sep=""))[2,1] + c(-1,1)*get(paste("b", i, sep=""))[2,2]*qt(0.975, modellist[[i]]$Df), 3)[1]), ", ", c(signif(get(paste("b", i, sep=""))[1,1] + c(-1,1)*get(paste("b", i, sep=""))[1,2]*qt(0.975, modellist[[i]]$Df), 3)[2], signif(get(paste("b", i, sep=""))[2,1] + c(-1,1)*get(paste("b", i, sep=""))[2,2]*qt(0.975, modellist[[1]]$Df), 3)[2]), "]", sep = ""))
    assign(paste("t", i, sep = ""), signif(get(paste("b", i, sep=""))[,3], 3))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$Df,each=2))
    assign(paste("p", i, sep = ""), signif(get(paste("b", i, sep=""))[,4], 3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(modellist[[i]]$nomY, ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rownames(complete) <- c(row.names(summary(modellist[[i]])$Points)[1], row.names(summary(modellist[[i]])$Points)[2])
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models.ss <- list(integrate1.ss, integrate2.ss)
sstable(models.ss, "Table 4b Simple Slopes")
```
