---
title: "Study 3a"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: default
---

## (1) Description of Data

The posted data for this study consists of 1 compiled, deidentified data file. This data file does not include data from an additional 284 respondents either because they did not complete the study, they completed the study more than once, or it was not possible to accurately match their separate survey sheets.

```{r include=FALSE}
options(width=100)

library(RCurl)
library(plyr)
library(ggplot2)
library(pequod)
library(psych)
library(data.table)
library(rtf)
library(pwr)


## DATA PREPARATION ##
csv <- getURL("https://raw.githubusercontent.com/abrowman/ism-jpsp2017/master/Study%203a/ISM_Study3a.csv")
mydata <- read.csv(textConnection(csv))
attach(mydata)

# score measures
rfqpro <- ((6-RFQpro1r)+RFQpro2+RFQpro3+(6-RFQpro4r)+RFQpro5+(6-RFQpro6r))/6
rfqpre <- ((6-RFQpre1r)+(6-RFQpre2r)+RFQpre3+(6-RFQpre4r)+(6-RFQpre5r))/5
rfq <- rfqpro-rfqpre
rfq_c <- scale(rfq,scale=F,center=T)

rfapro <- (rfapro2+rfapro3+rfapro4+rfapro5)/4
rfapre <- (rfapre1+rfapre2+rfapre3+rfapre5)/4
rfa <- rfapro-rfapre
rfa_c <- scale(rfa,scale=F,center=T)

rfbpro <- (rfbpro2+rfbpro3+rfbpro4+rfbpro5)/4
rfbpre <- (rfbpre1+rfbpre2+rfbpre3+rfbpre5)/4
rfb <- rfbpro-rfbpre
rfb_c <- scale(rfb,scale=F,center=T)

rf.dif <- abs(rfa-rfb)

central.sa1_c <- scale(central.sa1, scale=F, center=T)
central.sa2_c <- scale(central.sa2, scale=F, center=T)
cent.dif <- abs(central.sa1-central.sa2)
cent.dif_c <- scale(cent.dif,scale=F,center=T)
```


## (2) Descriptive Statistics

**Total *N*:** `r nrow(mydata)`

**Sensitivity analysis:** This sample provided a statistical power of .80 to detect effects of *f*^2^ >= `r round(pwr.f2.test(u = 1, v = nrow(mydata)-2, sig.level = .05, power = .80)$f2, digits = 3)`.

**Percentage by gender:**
```{r echo=FALSE}
Gender <- factor(ifelse(gender==1, "male", ifelse(gender==2, "female", NA)))
table(Gender, useNA="always")
```

***M*s and *SD*s:**
```{r echo=FALSE}
describe(data.frame(age, rfa, rfapro, rfapre, rfb, rfbpro, rfbpre, rfq, rfqpro, rfqpre, central.sa1, central.sa2, cent.dif, rf.dif))[c(2,3,4)]
```

**Alphas:**

* **Identity-specific motivation-A promotion:** `r round(alpha(data.frame(rfapro2,rfapro3,rfapro4,rfapro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-A prevention:** `r round(alpha(data.frame(rfapre1,rfapre2,rfapre3,rfapre5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-B promotion:** `r round(alpha(data.frame(rfbpro2,rfbpro3,rfbpro4,rfbpro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-B prevention:** `r round(alpha(data.frame(rfbpre1,rfbpre2,rfbpre3,rfbpre5))$total$raw_alpha, digits=2)`  
* **RFQ promotion:** `r round(alpha(data.frame((6-RFQpro1r),RFQpro2,RFQpro3,(6-RFQpro4r),RFQpro5,(6-RFQpro6r)))$total$raw_alpha, digits=2)`  
* **RFQ prevention:** `r round(alpha(data.frame((6-RFQpre1r),(6-RFQpre2r),RFQpre3,(6-RFQpre4r),(6-RFQpre5r)))$total$raw_alpha, digits=2)`


## (3) Correlations

**Correlations:**
```{r echo=FALSE}
corlist <- data.frame(rfa,rfb,rfq,rf.dif,cent.dif)
cortable <- data.frame(round(corr.test(as.matrix(corlist))$ci[c(1,2,5,10),1:3], digits=2), round(corr.test(as.matrix(corlist))$ci[c(1,2,5,10),4], digits=4), corr.test(as.matrix(corlist))$n[c(2,3,8,20)]-2)
colnames(cortable) <- c("lower","r","upper","p","df")
cortable
```


## (4) Main Analyses

### Regressing on identity-specific motivation-A on identity-specific motivation-B, difference in centrality, and their interaction

**Main effects (Step 1)**
```{r echo=FALSE}
summary(main1 <- lm(rfa ~ rfb_c + cent.dif_c))
```

**Step 1 CIs**
```{r echo=FALSE}
round(confint(main1, level = 0.95), digits=2)
```

**Interaction term added (Step 2)**
```{r echo=FALSE}
summary(integrate1 <- lm(rfa ~ rfb_c * cent.dif_c))
```

**Step 2 CIs**
```{r echo=FALSE}
round(confint(integrate1, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for interaction term:** `r round((summary(integrate1)$r.squared-summary(lm(rfa ~ rfb_c + cent.dif_c))$r.squared)/(1-summary(integrate1)$r.squared), digits=3)`

**Simple slopes**
```{r echo=FALSE}
integrate1.lmres <- lmres(rfa ~ rfb_c * cent.dif_c, mydata)
summary(integrate1.ss <- simpleSlope(integrate1.lmres, pred="rfb_c", mod1="cent.dif_c"))
```

**CIs among those with high identity incompatibility:** `r round(integrate1.ss$simple_slope[1,1] + c(-1,1)*integrate1.ss$simple_slope[1,2]*qt(0.975, integrate1.ss$Df), digits=2)`  

**CIs among those with low identity incompatibility:** `r round(integrate1.ss$simple_slope[2,1] + c(-1,1)*integrate1.ss$simple_slope[2,2]*qt(0.975, integrate1.ss$Df), digits=2)`


### Regressing on identity-specific motivation-B on identity-specific motivation-A, difference in centrality, and their interaction

**Main effects (Step 1)**
```{r echo=FALSE}
summary(main2 <- lm(rfb ~ rfa_c + cent.dif_c))
```

**Step 1 CIs**
```{r echo=FALSE}
round(confint(main2, level = 0.95), digits=2)
```

**Interaction term added (Step 2)**
```{r echo=FALSE}
summary(integrate2 <- lm(rfb ~ rfa_c * cent.dif_c))
```

**Step 2 CIs**
```{r echo=FALSE}
round(confint(integrate2, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for interaction term:** `r round((summary(integrate2)$r.squared-summary(lm(rfb ~ rfa_c + cent.dif_c))$r.squared)/(1-summary(integrate2)$r.squared), digits=3)`

**Simple slopes**
```{r echo=FALSE}
integrate2.lmres <- lmres(rfb ~ rfa_c * cent.dif_c, mydata)
summary(integrate2.ss <- simpleSlope(integrate2.lmres, pred="rfa_c", mod1="cent.dif_c"))
```

**CIs among those with high identity incompatibility:** `r round(integrate2.ss$simple_slope[1,1] + c(-1,1)*integrate2.ss$simple_slope[1,2]*qt(0.975, integrate2.ss$Df), digits=2)`  

**CIs among those with low identity incompatibility:** `r round(integrate2.ss$simple_slope[2,1] + c(-1,1)*integrate2.ss$simple_slope[2,2]*qt(0.975, integrate2.ss$Df), digits=2)`


## (5) Figure

```{r echo=FALSE}
plot.points <- data.frame(c("bLo cent.dif","bLo cent.dif","aHi cent.dif","aHi cent.dif"), c("aLo rfb","bHi rfb","aLo rfb","bHi rfb"), c(integrate1.ss$Points[1,1], integrate1.ss$Points[1,2], integrate1.ss$Points[2,1], integrate1.ss$Points[2,2]), c(integrate1.ss$simple_slope[1,2], integrate1.ss$simple_slope[1,2], integrate1.ss$simple_slope[2,2], integrate1.ss$simple_slope[2,2]))
colnames(plot.points) <- c("cent.dif","rfb","rfa","se")
limits <- aes(ymax = rfa + se, ymin = rfa - se)

plot1 <- ggplot(data=plot.points, aes(x=rfb, y=rfa, linetype=cent.dif)) + # data to plot
  geom_line(aes(group = cent.dif)) + # add regression line
  geom_errorbar(limits, width=.1) +
  theme_bw(base_family = "Arial", base_size = 14) + # font and font size
  theme(legend.position = c(.21,.95)) + # legend position
  theme(legend.key = element_blank()) + # no border around legend
  theme(legend.title = element_blank()) + # remove legend title
  scale_linetype_discrete(breaks=c("bLo cent.dif", "aHi cent.dif"), labels=c("Lower identity incompatibility (-1 SD)", "Higher identity incompatibility (+1 SD)")) +
  theme(axis.title.x = element_blank()) + # move x-axis label lower
  theme(axis.title.y = element_text(vjust=1.3)) + # move y-axis label left
  theme(panel.grid.minor = element_blank()) + # no grids
  theme(panel.grid.major = element_blank()) + # no borders
  theme(panel.border = element_blank()) + # removes default grey axis lines
  theme(axis.line = element_line(color = 'black')) + # put axis lines back, but in black
  coord_cartesian(ylim=c(-.6, .9)) + # y-axis range
  scale_x_discrete("", labels = c("aLo rfb"="Prevention-focused\n identity #2 (-1 SD)", "bHi rfb"="Promotion-focused\n identity #2 (+1 SD)")) + # x-axis titles
  scale_y_continuous("Promotion focus of identity #1", breaks = seq(-.6, .9, by=.3)) + # y-axis titles and range
  annotate("text", x=2.5, y=.88, label="(a)")
plot1
ggsave('Figure 3a.png', width=9, height=6, unit='in', dpi=300)
```

```{r include=FALSE}
## Scripts for producing tables

# Tables of full models
regtable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), round(coef(summary(modellist[[i]])), digits=3))
    assign(paste("ci", i, sep = ""), paste(round(get(paste("b", i, sep=""))[, 1], digits=2), " [", round(confint(modellist[[i]], level = 0.95)[,1], digits=2), ", ", round(confint(modellist[[i]], level = 0.95)[,2], digits=2), "]", sep = ""))
    assign(paste("t", i, sep = ""), round(summary(modellist[[i]])$coefficients[,3], digits=2))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$df[2],each=1+length(labels(modellist[[1]]))))
    assign(paste("p", i, sep = ""), round(summary(modellist[[i]])$coefficients[,4], digits=3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(all.vars(summary(modellist[[i]])$call)[1], ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rnames <- c("Intercept")
  for (j in 1:length(labels(modellist[[1]]))) {
    rnames <- append(rnames, labels(modellist[[1]])[j])
  }
  rownames(complete) <- rnames
  complete <- complete[-1,]
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)  # this can be an .rtf or a .doc
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models <- list(main1, main2)
regtable(models, "Table 4a Step 1")
models <- list(integrate1, integrate2)
regtable(models, "Table 4a Step 2")


# Tables for simple slopes
sstable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), signif(summary(modellist[[i]])$simple_slope))
    assign(paste("ci", i, sep = ""), paste(get(paste("b", i, sep=""))[, 1], " [", c(signif(get(paste("b", i, sep=""))[1,1] + c(-1,1)*get(paste("b", i, sep=""))[1,2]*qt(0.975, modellist[[i]]$Df), 3)[1], signif(get(paste("b", i, sep=""))[2,1] + c(-1,1)*get(paste("b", i, sep=""))[2,2]*qt(0.975, modellist[[i]]$Df), 3)[1]), ", ", c(signif(get(paste("b", i, sep=""))[1,1] + c(-1,1)*get(paste("b", i, sep=""))[1,2]*qt(0.975, modellist[[i]]$Df), 3)[2], signif(get(paste("b", i, sep=""))[2,1] + c(-1,1)*get(paste("b", i, sep=""))[2,2]*qt(0.975, modellist[[1]]$Df), 3)[2]), "]", sep = ""))
    assign(paste("t", i, sep = ""), signif(get(paste("b", i, sep=""))[,3], 3))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$Df,each=2))
    assign(paste("p", i, sep = ""), signif(get(paste("b", i, sep=""))[,4], 3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(modellist[[i]]$nomY, ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rownames(complete) <- c(row.names(summary(modellist[[i]])$Points)[1], row.names(summary(modellist[[i]])$Points)[2])
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models.ss <- list(integrate1.ss, integrate2.ss)
sstable(models.ss, "Table 4a Simple Slopes")
```
