---
title: "Study 1"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: default
---

## (1) Description of Data

The posted data for this study consists of 1 compiled, deidentified data file. Two (2) responses were excluded because it was not possible to accurately match their separate questionnaire sheets, as described in the main text of the article.

```{r include=FALSE}
options(width=100)

library(RCurl)
library(plyr)
library(psych)
library(data.table)
library(rtf)
library(pwr)

## DATA PREPARATION ##
csv <- getURL("https://raw.githubusercontent.com/abrowman/ism-jpsp2017/master/Study%201/ISM_Study1.csv")
mydata <- read.csv(textConnection(csv))

mydata$rfqpro2 <- as.numeric(gsub(7, NA, mydata$rfqpro2))
mydata$rfqpro2 <- as.numeric(gsub(6, NA, mydata$rfqpro2))
mydata$rfqpre3 <- as.numeric(gsub(7, NA, mydata$rfqpre3))
mydata$rfqpre4r <- as.numeric(gsub(6, NA, mydata$rfqpre4r))
mydata$rfqpre5r <- as.numeric(gsub(6, NA, mydata$rfqpre5r))
mydata$rfqpro4r <- as.numeric(gsub(22, 2, mydata$rfqpro4r))
mydata$rfqpro6r <- as.numeric(gsub(6, NA, mydata$rfqpro6r))
attach(mydata)

# score measures
rfqpro <- ((6-rfqpro1r)+rfqpro2+rfqpro3+(6-rfqpro4r)+rfqpro5+(6-rfqpro6r))/6
rfqpre <- ((6-rfqpre1r)+(6-rfqpre2r)+rfqpre3+(6-rfqpre4r)+(6-rfqpre5r))/5
rfq <- rfqpro-rfqpre
rfq_c <- scale(rfq,scale=F,center=T)

rfapro <- (RFApro2+RFApro3+RFApro4+RFApro5)/4
rfapre <- (RFApre1+RFApre2+RFApre3+RFApre5)/4
rfa <- rfapro-rfapre
rfa_c <- scale(rfa,scale=F,center=T)

rfhpro <- (RFHpro2+RFHpro3+RFHpro4+RFHpro5)/4
rfhpre <- (RFHpre1+RFHpre2+RFHpre3+RFHpre5)/4
rfh <- rfhpro-rfhpre
rfh_c <- scale(rfh,scale=F,center=T)

rfrpro <- (RFRpro2+RFRpro3+RFRpro4+RFRpro5)/4
rfrpre <- (RFRpre1+RFRpre2+RFRpre3+RFRpre5)/4
rfr <- rfrpro-rfrpre
rfr_c <- scale(rfr,scale=F,center=T)

achieve <- (Mot_Explore+Mot_Knowlege+Mot_Learn+Mot_Independent+Mot_Understand)/5
respons <- (Mot_GiveBack+Mot_Financial+Mot_Help+Mot_Honor+Mot_Rolemodel)/5
```


## (2) Descriptive Statistics

**Total *N*:**

* **Whole sample:** `r nrow(mydata)`  
* ***N* who completed Questionnaire A:** `r sum(questionnaire1, na.rm=T)`  
* ***N* who completed Questionnaire B:** `r sum(questionnaire2, na.rm=T)`

**Sensitivity analyses:** These completion rates provided a statistical power of .80 to detect effects of |*r*| >= `r round(pwr.r.test(n = sum(questionnaire1, na.rm=T), sig.level = .05, power = .80)$r, digits = 2)` and `r round(pwr.r.test(n = sum(questionnaire2, na.rm=T), sig.level = .05, power = .80)$r, digits = 2)`.

**Percentage by gender:**
```{r echo=FALSE}
gender <- factor(ifelse(Gender==1, "male", ifelse(Gender==2, "female", NA)))
table(gender, useNA="always")
```

***M*s and *SD*s:**
```{r echo=FALSE}
describe(data.frame(Age, rfa, rfapro, rfapre, rfh, rfhpro, rfhpre, rfr, rfrpro, rfrpre, rfq, rfqpro, rfqpre, achieve, respons))[c(2,3,4)]
```

**Alphas:**

* **Identity-specific motivation-academics promotion:** `r round(alpha(data.frame(RFApro2,RFApro3,RFApro4,RFApro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-academics prevention:** `r round(alpha(data.frame(RFApre1,RFApre2,RFApre3,RFApre5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-health promotion:** `r round(alpha(data.frame(RFHpro2,RFHpro3,RFHpro4,RFHpro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-health prevention:** `r round(alpha(data.frame(RFHpre1,RFHpre2,RFHpre3,RFHpre5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-relationship promotion:** `r round(alpha(data.frame(RFRpro2,RFRpro3,RFRpro4,RFRpro5))$total$raw_alpha, digits=2)`  
* **Identity-specific motivation-relationship prevention:** `r round(alpha(data.frame(RFRpre1,RFRpre2,RFRpre3,RFRpre5))$total$raw_alpha, digits=2)`  
* **RFQ promotion:** `r round(alpha(data.frame((6-rfqpro1r),rfqpro2,rfqpro3,(6-rfqpro4r),rfqpro5,(6-rfqpro6r)))$total$raw_alpha, digits=2)`  
* **RFQ prevention:** `r round(alpha(data.frame((6-rfqpre1r),(6-rfqpre2r),rfqpre3,(6-rfqpre4r),(6-rfqpre5r)))$total$raw_alpha, digits=2)`  
* **Achievement motives:** `r round(alpha(data.frame(Mot_Explore,Mot_Knowlege,Mot_Learn,Mot_Independent,Mot_Understand))$total$raw_alpha, digits=2)`  
* **Responsibility motives:** `r round(alpha(data.frame(Mot_GiveBack,Mot_Financial,Mot_Help,Mot_Honor,Mot_Rolemodel))$total$raw_alpha, digits=2)`


## (3) Zero-Order and Disattenuated Correlations

**Pairwise correlations:**
```{r echo=FALSE}
corlist <- data.frame(achieve,respons,rfa,rfh,rfr,rfq)
cortable1 <- data.frame(round(corr.test(as.matrix(corlist))$ci[10:15,1:3], digits=2), round(corr.test(as.matrix(corlist))$ci[10:15,4], digits=3), corr.test(as.matrix(corlist))$n[c(16,17,18,23,24,30)]-2)
colnames(cortable1) <- c("lower","r","upper","p","df")
cortable1
```

**Disattenuated correlations (above the horizontal; pairwise below the horizontal, alphas on the horizontal):**
```{r echo=FALSE}
a.rfa <- data.frame(RFApro2,RFApro3,RFApro4,RFApro5,RFApre1,RFApre2,RFApre3,RFApre5)
a.rfr <- data.frame(RFRpro2,RFRpro3,RFRpro4,RFRpro5,RFRpre1,RFRpre2,RFRpre3,RFRpre5)
a.rfh <- data.frame(RFHpro2,RFHpro3,RFHpro4,RFHpro5,RFHpre1,RFHpre2,RFHpre3,RFHpre5)
a.rfq <- data.frame((6-rfqpro1r),rfqpro2,rfqpro3,(6-rfqpro4r),rfqpro5,(6-rfqpro6r),(6-rfqpre1r),(6-rfqpre2r),rfqpre3,(6-rfqpre4r),(6-rfqpre5r))
alpha.rfa <- alpha(a.rfa)
alpha.rfr <- alpha(a.rfr)
alpha.rfh <- alpha(a.rfh)
alpha.rfq <- alpha(a.rfq)

x <- matrix(c(rfa,rfh,rfr,rfq),ncol=4)
x.cor <- cor(x, use="pairwise.complete.obs")
colnames(x.cor) <- c("rfa","rfh","rfr","rfq")
rownames(x.cor) <- c("rfa","rfh","rfr","rfq")
alpha <- c(alpha.rfa$total$raw_alpha, alpha.rfh$total$raw_alpha, alpha.rfr$total$raw_alpha, alpha.rfq$total$raw_alpha)
round(correct.cor(x.cor,alpha),2)
```


## (4) Factor Analyses

**Scree plot:**  
```{r echo=FALSE}
eigen.data <- data.frame(RFApro2,RFApro3,RFApro4,RFApro5,RFApre1,RFApre2,RFApre3,RFApre5,RFHpro2,RFHpro3,RFHpro4,RFHpro5,RFHpre1,RFHpre2,RFHpre3,RFHpre5,RFRpro2,RFRpro3,RFRpro4,RFRpro5,RFRpre1,RFRpre2,RFRpre3,RFRpre5)
eigen <- eigen(cor(eigen.data, use="complete.obs")) # calculate eigenvalues
plot(eigen$values, xlab="Factor number", ylab="Eigenvalue") # plot eigens
```

**Eigenvalues:**
```{r echo=FALSE}
round(eigen$values, digits=2)
```

**Factor analysis results:**
```{r echo=FALSE}
print(factanal(~RFApro2+RFApro3+RFApro4+RFApro5+RFApre1+RFApre2+RFApre3+RFApre5+RFHpro2+RFHpro3+RFHpro4+RFHpro5+RFHpre1+RFHpre2+RFHpre3+RFHpre5+RFRpro2+RFRpro3+RFRpro4+RFRpro5+RFRpre1+RFRpre2+RFRpre3+RFRpre5, factors=3)$loadings, cutoff=0)
```


## (5) Main Analyses

### Correlations between RFs and academic motives

**Correlations:**
```{r echo=FALSE}
cortable2 <- data.frame(round(corr.test(as.matrix(corlist))$ci[2:9,1:3], digits=2), round(corr.test(as.matrix(corlist))$ci[2:9,4], digits=3), corr.test(as.matrix(corlist))$n[c(3,4,5,6,9,10,11,12)]-2)
colnames(cortable2) <- c("lower","r","upper","p","df")
cortable2
```


### Regressing on academic motives on all RFs measures

**Estimates and CIs for achievement motives: identity-specific motivations:**
```{r echo=FALSE}
summary(achieve.regress.ism <- lm(achieve ~ rfa_c + rfh_c + rfr_c))
round(confint(achieve.regress.ism, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for identity-specific motivation-student term:** `r round((summary(achieve.regress.ism)$r.squared-summary(lm(achieve ~ rfh_c + rfr_c))$r.squared)/(1-summary(achieve.regress.ism)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for identity-specific motivation-physical term:** `r round((summary(achieve.regress.ism)$r.squared-summary(lm(achieve ~ rfa_c + rfr_c))$r.squared)/(1-summary(achieve.regress.ism)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for identity-specific motivation-relational term:** `r round((summary(achieve.regress.ism)$r.squared-summary(lm(achieve ~ rfa_c + rfh_c))$r.squared)/(1-summary(achieve.regress.ism)$r.squared), digits=3)`  


**Estimates and CIs for achievement motives: identity-specific motivation-student & RFQ:**
```{r echo=FALSE}
summary(achieve.regress.rfq <- lm(achieve ~ rfa_c + rfq_c))
round(confint(achieve.regress.rfq, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for identity-specific motivation-student term:** `r round((summary(achieve.regress.rfq)$r.squared-summary(lm(achieve ~ rfq_c))$r.squared)/(1-summary(achieve.regress.rfq)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for RFQ term:** `r round((summary(achieve.regress.rfq)$r.squared-summary(lm(achieve ~ rfa_c))$r.squared)/(1-summary(achieve.regress.rfq)$r.squared), digits=3)`  


**Estimates and CIs for responsibility motives: Identity-specific motivations:**
```{r echo=FALSE}
summary(respons.regress.ism <- lm(respons ~ rfa_c + rfh_c + rfr_c))
round(confint(respons.regress.ism, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for identity-specific motivation-student term:** `r round((summary(respons.regress.ism)$r.squared-summary(lm(respons ~ rfh_c + rfr_c))$r.squared)/(1-summary(respons.regress.ism)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for identity-specific motivation-physical term:** `r round((summary(respons.regress.ism)$r.squared-summary(lm(respons ~ rfa_c + rfr_c))$r.squared)/(1-summary(respons.regress.ism)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for identity-specific motivation-relational term:** `r round((summary(respons.regress.ism)$r.squared-summary(lm(respons ~ rfa_c + rfh_c))$r.squared)/(1-summary(respons.regress.ism)$r.squared), digits=3)`  


**Estimates and CIs for responsibility motives: identity-specific mortivation-student & RFQ:**
```{r echo=FALSE}
summary(respons.regress.rfq <- lm(respons ~ rfa_c + rfq_c))
round(confint(respons.regress.rfq, level = 0.95), digits=2)
```

***f*<sup>2</sup> value (effect size) for identity-specific motivation-student term:** `r round((summary(respons.regress.rfq)$r.squared-summary(lm(respons ~ rfq_c))$r.squared)/(1-summary(respons.regress.rfq)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for RFQ term:** `r round((summary(respons.regress.rfq)$r.squared-summary(lm(respons ~ rfa_c))$r.squared)/(1-summary(respons.regress.rfq)$r.squared), digits=3)`  


```{r include=FALSE, warning=FALSE}
## Create and export tables ##
regtable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), round(coef(summary(modellist[[i]])), digits=3))
    assign(paste("ci", i, sep = ""), paste(round(get(paste("b", i, sep=""))[, 1], digits=2), " [", round(confint(modellist[[i]], level = 0.95)[,1], digits=2), ", ", round(confint(modellist[[i]], level = 0.95)[,2], digits=2), "]", sep = ""))
    assign(paste("t", i, sep = ""), round(summary(modellist[[i]])$coefficients[,3], digits=2))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$df[2],each=1+length(labels(modellist[[1]]))))
    assign(paste("p", i, sep = ""), round(summary(modellist[[i]])$coefficients[,4], digits=3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(all.vars(summary(modellist[[i]])$call)[1], ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rnames <- c("Intercept")
  for (j in 1:length(labels(modellist[[1]]))) {
    rnames <- append(rnames, labels(modellist[[1]])[j])
  }
  rownames(complete) <- rnames
  complete <- complete[-1,]
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)  # this can be an .rtf or a .doc
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models1 <- list(achieve.regress.ism, respons.regress.ism)
regtable(models1, "Table 2a")
models2 <- list(achieve.regress.rfq, respons.regress.rfq)
regtable(models2, "Table 2b")
```
