---
title: "Study 4"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: default
---

## (1) Description of Data

The posted data for this study consists of 1 compiled, deidentified data file.

```{r include=FALSE}
options(width=100)

library(RCurl)
library(plyr)
library(ggplot2)
library(pequod)
library(psych)
library(data.table)
library(rtf)
library(pwr)

## DATA PREPARATION ##
csv <- getURL("https://raw.githubusercontent.com/abrowman/ism-jpsp2017/master/Study%204/ISM_Study4.csv")
mydata <- read.csv(textConnection(csv))
attach(mydata)

# calculate scores
rf1pro <- (rfapro2+rfapro3+rfapro4+rfapro5)/4
rf1pre <- (rfapre1+rfapre2+rfapre3+rfapre5)/4
rf1 <- rf1pro-rf1pre
rf1_c <- scale(rf1,scale=F,center=T)

rf2pro <- (rfbpro2+rfbpro3+rfbpro4+rfbpro5)/4
rf2pre <- (rfbpre1+rfbpre2+rfbpre3+rfbpre5)/4
rf2 <- rf2pro-rf2pre
rf2_c <- scale(rf2,scale=F,center=T)

pro.motives <- (ideal + growth + idealself + attain + eager + pursueopp + desirable)/7
pre.motives <- (ought + security + oughtself + maintain + cautious + vigilant + missopp + mistake + feasible)/9

pro.emo <- ((10-happy) + disappoint + (10-satis) + low + sad + discourage)/6
pre.emo <- (tense + agit + (10-calm) + onedge + uneasy + (10-relax))/6

stratcount <- rowSums(subset(mydata, select=strategies_1_TEXT:strategies_10_TEXT)!="")

pro.strat1 <- rowSums(subset(mydata, select=stratpro1_1:stratpro1_10), na.rm=T)/rowSums(!is.na(subset(mydata, select=stratpro1_1:stratpro1_10)))
pro.strat2 <- rowSums(subset(mydata, select=stratpro2_1:stratpro2_10), na.rm=T)/rowSums(!is.na(subset(mydata, select=stratpro2_1:stratpro2_10)))
pro.strat <- (pro.strat1+pro.strat2)/2

pre.strat1 <- rowSums(subset(mydata, select=stratpre1_1:stratpre1_10), na.rm=T)/rowSums(!is.na(subset(mydata, select=stratpre1_1:stratpre1_10)))
pre.strat2 <- rowSums(subset(mydata, select=stratpre2_1:stratpre2_10), na.rm=T)/rowSums(!is.na(subset(mydata, select=stratpre2_1:stratpre2_10)))
pre.strat <- (pre.strat1+pre.strat2)/2

abstract.strat <- rowSums(subset(mydata, select=strat.feas_1:strat.feas_10), na.rm=T)/rowSums(!is.na(subset(mydata, select=strat.feas_1:strat.feas_10)))

pro.counter <- (rowSums(subset(mydata, select=counter2_1:counter2_10)==1, na.rm=T)/rowSums(!is.na(subset(mydata, select=counter2_1:counter2_10))))*100
pre.counter <- (rowSums(subset(mydata, select=counter2_1:counter2_10)==2, na.rm=T)/rowSums(!is.na(subset(mydata, select=counter2_1:counter2_10))))*100

cond_c <- scale(cond, scale=F, center=T)
```


## (2) Descriptive Statistics

**Total *N*:** `r nrow(mydata)`

**Sensitivity analysis:** This sample provided a statistical power of .80 to detect effects of *f*^2^ >= `r round(pwr.f2.test(u = 1, v = nrow(mydata)-2, sig.level = .05, power = .80)$f2, digits = 3)`.

**Percentage by gender:**
```{r echo=FALSE}
Gender <- factor(ifelse(gender==1, "male", ifelse(gender==2, "female", NA)))
table(Gender, useNA="always")
```

***N* in each condition:**
```{r echo=FALSE}
table(cond, useNA="always")
```

***M*s and *SD*s:**
```{r echo=FALSE}
describe(data.frame(age, rf1, rf1pro, rf1pre, rf2, rf2pro, rf2pre, pro.motives, pre.motives, pro.strat, pre.strat, abstract.strat, pro.counter, pro.emo, pre.emo, abs(rf1-rf2)))[c(2,3,4)]
```

**Internal consistencies of measures:**

  * **SASRF-1 promotion:** $\alpha$ = `r round(alpha(data.frame(rfapro2,rfapro3,rfapro4,rfapro5))$total$raw_alpha, digits=2)`  
  * **SASRF-1 prevention:** $\alpha$ = `r round(alpha(data.frame(rfapre1,rfapre2,rfapre3,rfapre5))$total$raw_alpha, digits=2)`  
  * **SASRF-2 promotion:** $\alpha$ = `r round(alpha(data.frame(rfbpro2,rfbpro3,rfbpro4,rfbpro5))$total$raw_alpha, digits=2)`  
  * **SASRF-2 prevention:** $\alpha$ = `r round(alpha(data.frame(rfbpre1,rfbpre2,rfbpre3,rfbpre5))$total$raw_alpha, digits=2)`
  * **Promotion motives:** $\alpha$ = `r round(alpha(data.frame(ideal, growth, idealself, attain, eager, pursueopp, desirable))$total$raw_alpha, digits=2)`  
  * **Prevention motives:** $\alpha$ = `r round(alpha(data.frame(ought, security, oughtself, maintain, cautious, vigilant, missopp, mistake, feasible))$total$raw_alpha, digits=2)`  
  * **Promotion strategies:** *r*(`r round(cor.test(pro.strat1, pro.strat2)$parameter, digits=2)`) = `r round(cor.test(pro.strat1, pro.strat2)$estimate, digits=2)`, *p* = `r cor.test(pro.strat1, pro.strat2)$p.value`
  * **Prevention strategies:** *r*(`r round(cor.test(pre.strat1, pre.strat2)$parameter, digits=2)`) = `r round(cor.test(pre.strat1, pre.strat2)$estimate, digits=2)`, *p* = `r cor.test(pre.strat1, pre.strat2)$p.value`  
  * **Negative promotion emotions:** $\alpha$ = `r round(alpha(data.frame((10-happy), disappoint, (10-satis), low, sad, discourage))$total$raw_alpha, digits=2)`  
  * **Negative prevention emotions:** $\alpha$ = `r round(alpha(data.frame(tense, agit, (10-calm), onedge, uneasy, (10-relax)))$total$raw_alpha, digits=2)`  


## (3) Random assignment checks

**(a) Unequal variance test, *t*-test, and *M*s and *SD*s for: SAS-REG-1**
```{r echo=FALSE}
var.test(rf1~cond)
t.test(rf1~cond, var.equal=FALSE)
describeBy(rf1, cond)
```

**(b) Unequal variance test, *t*-test, and *M*s and *SD*s for: SAS-REG-2**
```{r echo=FALSE}
var.test(rf2~cond)
t.test(rf2~cond, var.equal=TRUE)
describeBy(rf2, cond)
```


## (4) Primary Analyses

### Explicit promotion motives

**Step 1:**
```{r echo=FALSE}
summary(pro.motives.main <- lm(pro.motives ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pro.motives.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pro.motives.regress <- lm(pro.motives ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pro.motives.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(pro.motives.regress)$r.squared-summary(lm(pro.motives ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pro.motives.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for interaction term with rf2:** `r round((summary(pro.motives.regress)$r.squared-summary(lm(pro.motives ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pro.motives.regress)$r.squared), digits=3)`


### Explicit prevention motives

**Step 1:**
```{r echo=FALSE}
summary(pre.motives.main <- lm(pre.motives ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pre.motives.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pre.motives.regress <- lm(pre.motives ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pre.motives.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(pre.motives.regress)$r.squared-summary(lm(pre.motives ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pre.motives.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for interaction term with rf2:** `r round((summary(pre.motives.regress)$r.squared-summary(lm(pre.motives ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pre.motives.regress)$r.squared), digits=3)`


### Preferred strategies (promotion-focused)

**Step 1:**
```{r echo=FALSE}
summary(pro.strat.main <- lm(pro.strat ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pro.strat.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pro.strat.regress <- lm(pro.strat ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pro.strat.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(pro.strat.regress)$r.squared-summary(lm(pro.strat ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pro.strat.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for the interaction term with rf2:** `r round((summary(pro.strat.regress)$r.squared-summary(lm(pro.strat ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pro.strat.regress)$r.squared), digits=3)`


### Preferred strategies (prevention-focused)

**Step 1:**
```{r echo=FALSE}
summary(pre.strat.main <- lm(pre.strat ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pre.strat.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pre.strat.regress <- lm(pre.strat ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pre.strat.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r (summary(pre.strat.regress)$r.squared-summary(lm(pre.strat ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pre.strat.regress)$r.squared)`  

***f*<sup>2</sup> value (effect size) for the interaction term with rf2:** `r round((summary(pre.strat.regress)$r.squared-summary(lm(pre.strat ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pre.strat.regress)$r.squared), digits=3)`


### Abstractness of preferred strategies

**Step 1:**
```{r echo=FALSE}
summary(abstract.strat.main <- lm(abstract.strat ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(abstract.strat.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(abstract.strat.regress <- lm(abstract.strat ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(abstract.strat.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(abstract.strat.regress)$r.squared-summary(lm(abstract.strat ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(abstract.strat.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for the interaction term with rf2:** `r round((summary(abstract.strat.regress)$r.squared-summary(lm(abstract.strat ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(abstract.strat.regress)$r.squared), digits=3)`


### Promotion-relevant emotional responses

**Step 1:**
```{r echo=FALSE}
summary(pro.emo.main <- lm(pro.emo ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pro.emo.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pro.emo.regress <- lm(pro.emo ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pro.emo.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(pro.emo.regress)$r.squared-summary(lm(pro.emo ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pro.emo.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for the interaction term with rf2:** `r round((summary(pro.motives.regress)$r.squared-summary(lm(pro.emo ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pro.motives.regress)$r.squared), digits=3)`


### Prevention-relevant emotional responses

**Step 1:**
```{r echo=FALSE}
summary(pre.emo.main <- lm(pre.emo ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pre.emo.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pre.emo.regress <- lm(pre.emo ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pre.emo.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(pre.emo.regress)$r.squared-summary(lm(pre.emo ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pre.emo.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for the interaction term with rf2:** `r round((summary(pre.motives.regress)$r.squared-summary(lm(pre.emo ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pre.motives.regress)$r.squared), digits=4)`


### Counterfactual thinking

**Step 1:**
```{r echo=FALSE}
summary(pro.counter.main <- lm(pro.counter ~ cond_c + rf1_c + rf2_c))
```

**Step 1 *CI*s:**
```{r echo=FALSE}
round(confint(pro.counter.main, level = 0.95), digits = 2)
```

**Step 2:**
```{r echo=FALSE}
summary(pro.counter.regress <- lm(pro.counter ~ cond_c * rf1_c + cond_c * rf2_c))
```

**Step 2 *CI*s:**
```{r echo=FALSE}
round(confint(pro.counter.regress, level = 0.95), digits = 2)
```

***f*<sup>2</sup> value (effect size) for the interaction term with rf1:** `r round((summary(pro.counter.regress)$r.squared-summary(lm(pro.counter ~ cond_c + rf1_c + cond_c * rf2_c))$r.squared)/(1-summary(pro.counter.regress)$r.squared), digits=3)`  

***f*<sup>2</sup> value (effect size) for the interaction term with rf2:** `r round((summary(pro.counter.regress)$r.squared-summary(lm(pro.counter ~ cond_c * rf1_c + cond_c + rf2_c))$r.squared)/(1-summary(pro.counter.regress)$r.squared), digits=4)`


```{r echo=FALSE}
## scripts for producing tables
regtable <- function(modellist, docname) {
  sections <- list(NA)
  colnam <- vector("list", length(modellist)*4)
  for (i in 1:length(modellist)) {
    assign(paste("b", i, sep = ""), round(coef(summary(modellist[[i]])), digits=3))
    assign(paste("ci", i, sep = ""), paste(round(get(paste("b", i, sep=""))[, 1], digits=2), " [", round(confint(modellist[[i]], level = 0.95)[,1], digits=2), ", ", round(confint(modellist[[i]], level = 0.95)[,2], digits=2), "]", sep = ""))
    assign(paste("t", i, sep = ""), round(summary(modellist[[i]])$coefficients[,3], digits=2))
    assign(paste("df", i, sep = ""), rep(summary(modellist[[i]])$df[2],each=1+length(labels(modellist[[1]]))))
    assign(paste("p", i, sep = ""), round(summary(modellist[[i]])$coefficients[,4], digits=3))
    assign(paste("section", i, sep = ""), rbind(cbind(get(paste("ci", i, sep = "")), get(paste("t", i, sep = "")), get(paste("df", i, sep = "")), get(paste("p", i, sep = "")))))
    sections[[i]] <- get(paste("section", i, sep = ""))
    colnam[1+(4*(i-1))] <- paste(all.vars(summary(modellist[[i]])$call)[1], ": b (95% CIs)", sep="")
    colnam[2+(4*(i-1))] <- "t"
    colnam[3+(4*(i-1))] <- "df"
    colnam[4+(4*(i-1))] <- "p"
  }
  complete <- do.call(cbind, sections)
  colnames(complete) <- colnam
  rnames <- c("Intercept")
  for (j in 1:length(labels(modellist[[1]]))) {
    rnames <- append(rnames, labels(modellist[[1]])[j])
  }
  rownames(complete) <- rnames
  complete <- complete[-1,]
  rtffile <- RTF(file=paste(docname, ".doc", sep=""), width=11, height=8.5, font.size=8)  # this can be an .rtf or a .doc
  addTable(rtffile, cbind(rownames(complete), complete), col.justify="C", header.col.justify="C")
  done(rtffile)
}
models1 <- list(pro.motives.main, pre.motives.main, pro.strat.main, pre.strat.main, abstract.strat.main, pro.emo.main, pre.emo.main, pro.counter.main)
regtable(models1, "Table 5 Step 1")
models2 <- list(pro.motives.regress, pre.motives.regress, pro.strat.regress, pre.strat.regress, abstract.strat.regress, pro.emo.regress, pre.emo.regress, pro.counter.regress)
regtable(models2, "Table 5 Step 2")
```
